Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-11 cordillera-cycle.tex
Update state of the manuscript.

\begin{center}
\begin{tabular}{>{\bfseries}ll}
    \tophline
    Introduction & Happy with it except for missing refs.\\
    Model setup  & Needs minor fixes to avoid repeating the previous paper.\\
    Results      & Almost happy with it. \\
    Discussion   & Large gaps still have to be filled.\\
    Conclusions  & Main contents are here but the text needs to be improved.\\
    Figures      & I have plans for a couple extra ones.\\
    \bottomhline
\end{tabular}
\end{center}

@@

\todo{Improve the style.}

>>>>

\begin{center}
\begin{tabular}{>{\bfseries}ll}
    \tophline
    Introduction & Happy with it except for missing refs.\\
    Model setup  & Happy with it except for missing refs.\\
    Results      & Happy with it except for missing refs.\\
    Discussion   & Deglaciation parts needs improvement.\\
    Conclusions  & Can be compacted and the style improved.\\
    \bottomhline
\end{tabular}
\end{center}

@@
